Effect of quality-adjusted production function inputs

### 2015-07-08 Articles/Article_EcolEcon_2015/EcolEcon_2015.tex
Redoing model names.
Rearranging text into paper order.

Both historical GDP and fitted GDP are shown in 
Figures~\ref{fig:Graphs CD-fitted}--\ref{fig:Graphs CESekl-fitted}.
%
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}[H]

@@

Figures~\ref{fig:Graphs CD-resid}--\ref{fig:Graphs CESekl-resid}
show fitting residuals for all models.
%
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}[H]

@@

@@

Table~\ref{tab:Effect_of_CST_CD} shows the effect of the CST 
on fitted parameters for the Cobb-Douglas model and the exponential-only model.
The Cobb-Douglas models show lower $mse$ than the exponential-only models.
The Cobb-Douglas models also reduce solow residual ($\lambda$) relative
to the exponential-only case.
%
% latex table generated in R 3.2.0 by xtable 1.7-4 package
% Wed Jul  8 15:28:27 2015
\begin{table}[ht]
\centering
\caption{Model parameters for Cobb-Douglas models with unadjusted factors of production, without energy.} 
\label{tab:Effect_of_CST_CD}
{\tiny
\begin{tabular}{lllrrrrr}
  \hline
Country & model & cst & scale & lambda & alpha\_1 & alpha\_2 & mse \\ 
  \hline
PT & exp & Reject CST & 1.283537 & 0.034507 & 0.000000 & 0.000000 & 0.013359 \\ 
  PT & CD & Adhere to CST & 1.328501 & 0.016080 & 0.300000 & 0.700000 & 0.011724 \\ 
  PT & CD & Reject CST & 1.113489 & $-$0.005539 & 1.000000 & 0.000000 & 0.003190 \\ 
  UK & exp & Reject CST & 1.021833 & 0.023565 & 0.000000 & 0.000000 & 0.001212 \\ 
  UK & CD & Adhere to CST & 1.032978 & 0.015510 & 0.300000 & 0.700000 & 0.000775 \\ 
  UK & CD & Reject CST & 1.000925 & 0.006654 & 0.544956 & 0.455044 & 0.000494 \\ 
   \hline
\end{tabular}
}
\end{table}

%
Table~\ref{tab:Effect_of_CST_CES} shows the effect of the CST 
on fitted parameters for the CES model.
The CES models show lower $mse$ than the exponential-only models.
The CES models also reduce solow residual ($\lambda$) relative
to the exponential-only case.
%
% latex table generated in R 3.2.0 by xtable 1.7-4 package
% Wed Jul  8 15:28:27 2015
\begin{table}[ht]
\centering
\caption{Model parameters for CES models with unadjusted factors of production, without energy.} 
\label{tab:Effect_of_CST_CES}
{\tiny
\begin{tabular}{lllrrrrrr}
  \hline
Country & model & cst & gamma & lambda & alpha\_1 & alpha\_2 & sigma\_1 & mse \\ 
  \hline
PT & exp & Reject CST &  & 0.034507 & 0.000000 & 0.000000 &  & 0.013359 \\ 
  PT & CES & Adhere to CST & 1.318284 & 0.018825 & 0.300000 & 0.700000 & 0.665163 & 0.011450 \\ 
  PT & CES & Reject CST & 0.998729 & 0.012404 & 0.983352 & 0.016648 & 0.173623 & 0.001113 \\ 
  UK & exp & Reject CST &  & 0.023565 & 0.000000 & 0.000000 &  & 0.001212 \\ 
  UK & CES & Adhere to CST & 1.006734 & 0.020914 & 0.300000 & 0.700000 & 0.509524 & 0.000491 \\ 
  UK & CES & Reject CST & 0.977872 & 0.017904 & 0.436298 & 0.563702 & 0.500000 & 0.000326 \\ 
   \hline
\end{tabular}
}
\end{table}

@@

To calculate $\Delta \lambda$ and $\Delta mse$, we need to fit all combinations of 
country, model, flavor, energy, nest, and CST.
Table~\ref{tab:CD_coeffs} shows coefficients for all fitted Cobb-Douglas models
and the reference model (exponential-only).
%
% latex table generated in R 3.2.0 by xtable 1.7-4 package
% Wed Jul  8 15:28:28 2015
\begin{table}[ht]
\centering
\caption{Model parameters for all Cobb-Douglas models.} 
\label{tab:CD_coeffs}
{\tiny
\begin{tabular}{lllllrrrrrr}
  \hline
Country & model & flavor & energy & cst & scale & lambda & alpha\_1 & alpha\_2 & alpha\_3 & mse \\ 
  \hline
PT & exp &  & Without energy & Reject CST & 1.283537 & 0.034507 & 0.000000 & 0.000000 & 0.000000 & 0.013359 \\ 
  PT & CD & Unadjusted & Without energy & Adhere to CST & 1.328501 & 0.016080 & 0.300000 & 0.700000 & 0.000000 & 0.011724 \\ 
  PT & CD & Unadjusted & Without energy & Reject CST & 1.113489 & $-$0.005539 & 1.000000 & 0.000000 & 0.000000 & 0.003190 \\ 
  PT & CD & Unadjusted & With energy & Reject CST & 1.130790 & $-$0.004439 & 0.755978 & 0.000000 & 0.244022 & 0.002628 \\ 
  PT & CD & Quality-adjusted & Without energy & Adhere to CST & 1.364226 & 0.004183 & 0.300000 & 0.700000 & 0.000000 & 0.011340 \\ 
  PT & CD & Quality-adjusted & Without energy & Reject CST & 1.231989 & $-$0.015079 & 1.000000 & 0.000000 & 0.000000 & 0.008937 \\ 
  PT & CD & Quality-adjusted & With energy & Reject CST & 1.111839 & $-$0.004569 & 0.000000 & 0.000000 & 1.000000 & 0.002268 \\ 
  UK & exp &  & Without energy & Reject CST & 1.021833 & 0.023565 & 0.000000 & 0.000000 & 0.000000 & 0.001212 \\ 
  UK & CD & Unadjusted & Without energy & Adhere to CST & 1.032978 & 0.015510 & 0.300000 & 0.700000 & 0.000000 & 0.000775 \\ 
  UK & CD & Unadjusted & Without energy & Reject CST & 1.000925 & 0.006654 & 0.544956 & 0.455044 & 0.000000 & 0.000494 \\ 
  UK & CD & Unadjusted & With energy & Reject CST & 0.995030 & 0.018134 & 0.162500 & 0.460325 & 0.377175 & 0.000331 \\ 
  UK & CD & Quality-adjusted & Without energy & Adhere to CST & 1.038384 & 0.008725 & 0.300000 & 0.700000 & 0.000000 & 0.001564 \\ 
  UK & CD & Quality-adjusted & Without energy & Reject CST & 1.015146 & $-$0.008149 & 0.751058 & 0.248942 & 0.000000 & 0.000720 \\ 
  UK & CD & Quality-adjusted & With energy & Reject CST & 0.970614 & 0.001981 & 0.403433 & 0.330248 & 0.266319 & 0.000453 \\ 
   \hline
\end{tabular}
}
\end{table}

%
Tables~\ref{tab:CES_coeffs} and~\ref{tab:CES_coeffs_sigmas} show 
coefficients for all fitted CES models and the reference model (exponential-only).
%
% latex table generated in R 3.2.0 by xtable 1.7-4 package
% Wed Jul  8 15:28:28 2015
\begin{table}[ht]
\centering
\caption{Model parameters for all CES models.} 
\label{tab:CES_coeffs}
{\tiny
\begin{tabular}{llllllrrrrr}
  \hline
Country & model & flavor & energy & nest & cst & gamma & lambda & alpha\_1 & alpha\_2 & alpha\_3 \\ 
  \hline
PT & exp &  & Without energy &  & Reject CST &  & 0.034507 & 0.000000 & 0.000000 & 0.000000 \\ 
  PT & CES & Unadjusted & Without energy & kl & Adhere to CST & 1.318284 & 0.018825 & 0.300000 & 0.700000 & 0.000000 \\ 
  PT & CES & Unadjusted & Without energy & kl & Reject CST & 0.998729 & 0.012404 & 0.983352 & 0.016648 & 0.000000 \\ 
  PT & CES & Unadjusted & With energy & kle & Reject CST & 1.022631 & 0.009738 & 0.727922 & 0.000064 & 0.272014 \\ 
  PT & CES & Unadjusted & With energy & lek & Reject CST & 1.005212 & 0.008318 & 1.000000 & 0.000000 & 0.000000 \\ 
  PT & CES & Unadjusted & With energy & ekl & Reject CST & 1.009966 & 0.010742 & 0.983292 & 0.016708 & 0.000000 \\ 
  PT & CES & Quality-adjusted & Without energy & kl & Adhere to CST & 1.335143 & 0.009131 & 0.300000 & 0.700000 & 0.000000 \\ 
  PT & CES & Quality-adjusted & Without energy & kl & Reject CST & 1.017672 & 0.005739 & 1.000000 & 0.000000 & 0.000000 \\ 
  PT & CES & Quality-adjusted & With energy & kle & Reject CST & 1.027582 & 0.004508 & 0.902835 & 0.000000 & 0.097165 \\ 
  PT & CES & Quality-adjusted & With energy & lek & Reject CST & 1.016454 & 0.005790 & 1.000000 & 0.000000 & 0.000000 \\ 
  PT & CES & Quality-adjusted & With energy & ekl & Reject CST & 1.017327 & 0.005789 & 1.000000 & 0.000000 & 0.000000 \\ 
  UK & exp &  & Without energy &  & Reject CST &  & 0.023565 & 0.000000 & 0.000000 & 0.000000 \\ 
  UK & CES & Unadjusted & Without energy & kl & Adhere to CST & 1.006734 & 0.020914 & 0.300000 & 0.700000 & 0.000000 \\ 
  UK & CES & Unadjusted & Without energy & kl & Reject CST & 0.977872 & 0.017904 & 0.436298 & 0.563702 & 0.000000 \\ 
  UK & CES & Unadjusted & With energy & kle & Reject CST & 0.989712 & 0.013857 & 0.445243 & 0.554757 & 0.000000 \\ 
  UK & CES & Unadjusted & With energy & lek & Reject CST & 0.982919 & 0.020230 & 0.570049 & 0.134387 & 0.295564 \\ 
  UK & CES & Unadjusted & With energy & ekl & Reject CST & 0.985088 & 0.022682 & 0.254298 & 0.738243 & 0.007460 \\ 
  UK & CES & Quality-adjusted & Without energy & kl & Adhere to CST & 1.008638 & 0.013592 & 0.300000 & 0.700000 & 0.000000 \\ 
  UK & CES & Quality-adjusted & Without energy & kl & Reject CST & 0.983725 & 0.001956 & 0.628728 & 0.371272 & 0.000000 \\ 
  UK & CES & Quality-adjusted & With energy & kle & Reject CST & 0.980315 & 0.007103 & 0.426684 & 0.421804 & 0.151512 \\ 
  UK & CES & Quality-adjusted & With energy & lek & Reject CST & 0.968799 & 0.007115 & 0.469167 & 0.144017 & 0.386817 \\ 
  UK & CES & Quality-adjusted & With energy & ekl & Reject CST & 0.981695 & 0.011338 & 0.305749 & 0.642022 & 0.052229 \\ 
   \hline
\end{tabular}
}
\end{table}

%
% latex table generated in R 3.2.0 by xtable 1.7-4 package
% Wed Jul  8 15:28:28 2015
\begin{table}[ht]
\centering
\caption{Model parameters for all CES models.} 
\label{tab:CES_coeffs_sigmas}
{\tiny
\begin{tabular}{llllllrrr}
  \hline
Country & model & flavor & energy & nest & cst & sigma\_1 & sigma & mse \\ 
  \hline
PT & exp &  & Without energy &  & Reject CST &  &  & 0.013359 \\ 
  PT & CES & Unadjusted & Without energy & kl & Adhere to CST & 0.665163 &  & 0.011450 \\ 
  PT & CES & Unadjusted & Without energy & kl & Reject CST & 0.173623 &  & 0.001113 \\ 
  PT & CES & Unadjusted & With energy & kle & Reject CST & 0.078512 & 1.747120 & 0.000746 \\ 
  PT & CES & Unadjusted & With energy & lek & Reject CST & 0.398887 & 0.013645 & 0.000588 \\ 
  PT & CES & Unadjusted & With energy & ekl & Reject CST & 0.005193 & 0.186281 & 0.000985 \\ 
  PT & CES & Quality-adjusted & Without energy & kl & Adhere to CST & 0.399944 &  & 0.009694 \\ 
  PT & CES & Quality-adjusted & Without energy & kl & Reject CST & 0.017511 &  & 0.000804 \\ 
  PT & CES & Quality-adjusted & With energy & kle & Reject CST & 0.017991 &     Inf & 0.000792 \\ 
  PT & CES & Quality-adjusted & With energy & lek & Reject CST & 0.017595 & 0.005358 & 0.000812 \\ 
  PT & CES & Quality-adjusted & With energy & ekl & Reject CST & 0.017013 &  & 0.000817 \\ 
  UK & exp &  & Without energy &  & Reject CST &  &  & 0.001212 \\ 
  UK & CES & Unadjusted & Without energy & kl & Adhere to CST & 0.509524 &  & 0.000491 \\ 
  UK & CES & Unadjusted & Without energy & kl & Reject CST & 0.500000 &  & 0.000326 \\ 
  UK & CES & Unadjusted & With energy & kle & Reject CST & 0.720815 & 0.009391 & 0.000223 \\ 
  UK & CES & Unadjusted & With energy & lek & Reject CST &     Inf & 0.465188 & 0.000289 \\ 
  UK & CES & Unadjusted & With energy & ekl & Reject CST & 0.103338 & 1.340508 & 0.000281 \\ 
  UK & CES & Quality-adjusted & Without energy & kl & Adhere to CST & 0.545219 &  & 0.001207 \\ 
  UK & CES & Quality-adjusted & Without energy & kl & Reject CST & 0.607601 &  & 0.000571 \\ 
  UK & CES & Quality-adjusted & With energy & kle & Reject CST & 0.611818 & 0.014357 & 0.000267 \\ 
  UK & CES & Quality-adjusted & With energy & lek & Reject CST &     Inf & 0.611994 & 0.000380 \\ 
  UK & CES & Quality-adjusted & With energy & ekl & Reject CST & 0.190138 & 1.247783 & 0.000301 \\ 
   \hline
\end{tabular}
}
\end{table}

%
Table~\ref{tab:DSRmse_CD} shows $\Delta \lambda$ and $\Delta mse$ results for the Cobb-Douglas models.
%
% latex table generated in R 3.2.0 by xtable 1.7-4 package
% Wed Jul  8 15:28:28 2015
\begin{table}[ht]
\centering
\caption{$\Delta \lambda$ and $\Delta mse$ for Cobb-Douglas models.} 
\label{tab:DSRmse_CD}
{\tiny
\begin{tabular}{lllllrr}
  \hline
Country & model & flavor & energy & cst & Dlambda & Dmse \\ 
  \hline
PT & CD & Unadjusted & Without energy & Adhere to CST & $-$0.018427 & $-$0.001635 \\ 
  PT & CD & Unadjusted & Without energy & Reject CST & $-$0.028968 & $-$0.010168 \\ 
  PT & CD & Unadjusted & With energy & Reject CST & $-$0.030068 & $-$0.010730 \\ 
  PT & CD & Quality-adjusted & Without energy & Adhere to CST & $-$0.030324 & $-$0.002019 \\ 
  PT & CD & Quality-adjusted & Without energy & Reject CST & $-$0.019428 & $-$0.004422 \\ 
  PT & CD & Quality-adjusted & With energy & Reject CST & $-$0.029938 & $-$0.011091 \\ 
  UK & CD & Unadjusted & Without energy & Adhere to CST & $-$0.008055 & $-$0.000437 \\ 
  UK & CD & Unadjusted & Without energy & Reject CST & $-$0.016911 & $-$0.000717 \\ 
  UK & CD & Unadjusted & With energy & Reject CST & $-$0.005432 & $-$0.000880 \\ 
  UK & CD & Quality-adjusted & Without energy & Adhere to CST & $-$0.014840 & 0.000352 \\ 
  UK & CD & Quality-adjusted & Without energy & Reject CST & $-$0.015416 & $-$0.000492 \\ 
  UK & CD & Quality-adjusted & With energy & Reject CST & $-$0.021584 & $-$0.000758 \\ 
   \hline
\end{tabular}
}
\end{table}

>>>>

Both historical GDP and fitted GDP are shown in 
Figures~\ref{fig:Graphs CESkle-fitted}--\ref{fig:Graphs CESekl-fitted}.
%
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}[H]

@@

Figures~\ref{fig:Graphs CESkle-resid}--\ref{fig:Graphs CESekl-resid}
show fitting residuals for all CES models.
%
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}[H]

@@

The primary results from this paper involve the effects of
the following modeling decisions:
rejecting (or adhering to) the cost share theorem,
quality-adjusting (or not) the factors of production,
including energy (or not) in the production function, and
nesting (in the CES model).

We evaluate the effects of these modeling decisions 
first on goodness of fit and Solow residual,
next on factor shares, and 
finally on factor substitutability.

%++++++++++++++++++++++++++++++
\subsection{Goodness of fit and Solow residual} 
\label{sec:fit_and_sr}
%++++++++++++++++++++++++++++++

%------------------------------
\subsubsection{Rejecting (or adhering to) the cost share theorem} 
\label{sec:gfsr_cst}
%------------------------------

%------------------------------
\subsubsection{Quality-adjusting (or not) factors of production} 
\label{sec:gfsr_fop}
%------------------------------

%------------------------------
\subsubsection{Including energy (or not)} 
\label{sec:gfsr_energy}
%------------------------------

%------------------------------
\subsubsection{CES nesting} 
\label{sec:gfsr_nesting}
%------------------------------

%++++++++++++++++++++++++++++++
\subsection{Factor shares} 
\label{sec:shares}
%++++++++++++++++++++++++++++++

%------------------------------
\subsubsection{Rejecting (or adhering to) the cost share theorem} 
\label{sec:fs_cst}
%------------------------------

%------------------------------
\subsubsection{Quality-adjusting (or not) factors of production} 
\label{sec:fs_fop}
%------------------------------

%------------------------------
\subsubsection{Including energy (or not)} 
\label{sec:fs_energy}
%------------------------------

%------------------------------
\subsubsection{CES nesting} 
\label{sec:fs_nesting}
%------------------------------

%++++++++++++++++++++++++++++++
\subsection{Factor substitutability} 
\label{sec:substitutability}
%++++++++++++++++++++++++++++++

%------------------------------
\subsubsection{Rejecting (or adhering to) the cost share theorem} 
\label{sec:sigma_cst}
%------------------------------

%------------------------------
\subsubsection{Quality-adjusting (or not) factors of production} 
\label{sec:sigma_fop}
%------------------------------

%------------------------------
\subsubsection{Including energy (or not)} 
\label{sec:sigma_energy}
%------------------------------

%------------------------------
\subsubsection{CES nesting} 
\label{sec:sigma_nesting}
%------------------------------

@@

Table~\ref{tab:Effect_of_CST_CES} shows the effect of the CST 
on fitted parameters for the CES model.
The CES models show lower $mse$ than the exponential-only models.
The CES models also reduce solow residual ($\lambda$) relative
to the exponential-only case.
%
% latex table generated in R 3.2.0 by xtable 1.7-4 package
% Wed Jul  8 16:46:02 2015
\begin{table}[ht]
\centering
\caption{Model parameters for CES models with unadjusted factors of production, without energy.} 
\label{tab:Effect_of_CST_CES}
{\tiny
\begin{tabular}{lllrrrrrr}
  \hline
Country & model & cst & gamma & lambda & alpha\_1 & alpha\_2 & sigma\_1 & mse \\ 
  \hline
PT & exp & Reject CST &  & 0.034507 & 0.000000 & 0.000000 &  & 0.013359 \\ 
  PT & CES & Adhere to CST & 1.318284 & 0.018825 & 0.300000 & 0.700000 & 0.665163 & 0.011450 \\ 
  PT & CES & Reject CST & 0.998729 & 0.012404 & 0.983352 & 0.016648 & 0.173623 & 0.001113 \\ 
  UK & exp & Reject CST &  & 0.023565 & 0.000000 & 0.000000 &  & 0.001212 \\ 
  UK & CES & Adhere to CST & 1.006734 & 0.020914 & 0.300000 & 0.700000 & 0.509524 & 0.000491 \\ 
  UK & CES & Reject CST & 0.977872 & 0.017904 & 0.436298 & 0.563702 & 0.500000 & 0.000326 \\ 
   \hline
\end{tabular}
}
\end{table}

@@

To calculate $\Delta \lambda$ and $\Delta mse$, we need to fit all combinations of 
country, model, flavor, energy, nest, and CST.
Tables~\ref{tab:CES_coeffs} and~\ref{tab:CES_coeffs_sigmas} show 
coefficients for all fitted CES models and the reference model (exponential-only).
%
% latex table generated in R 3.2.0 by xtable 1.7-4 package
% Wed Jul  8 16:46:02 2015
\begin{table}[ht]
\centering
\caption{Model parameters for all CES models.} 
\label{tab:CES_coeffs}
{\tiny
\begin{tabular}{llllllrrrrr}
  \hline
Country & model & flavor & energy & nest & cst & gamma & lambda & alpha\_1 & alpha\_2 & alpha\_3 \\ 
  \hline
PT & exp &  & Without energy &  & Reject CST &  & 0.034507 & 0.000000 & 0.000000 & 0.000000 \\ 
  PT & CES & Unadjusted & Without energy & kl & Adhere to CST & 1.318284 & 0.018825 & 0.300000 & 0.700000 & 0.000000 \\ 
  PT & CES & Unadjusted & Without energy & kl & Reject CST & 0.998729 & 0.012404 & 0.983352 & 0.016648 & 0.000000 \\ 
  PT & CES & Unadjusted & With energy & kle & Reject CST & 1.022631 & 0.009738 & 0.727922 & 0.000064 & 0.272014 \\ 
  PT & CES & Unadjusted & With energy & lek & Reject CST & 1.005212 & 0.008318 & 1.000000 & 0.000000 & 0.000000 \\ 
  PT & CES & Unadjusted & With energy & ekl & Reject CST & 1.009966 & 0.010742 & 0.983292 & 0.016708 & 0.000000 \\ 
  PT & CES & Quality-adjusted & Without energy & kl & Adhere to CST & 1.335143 & 0.009131 & 0.300000 & 0.700000 & 0.000000 \\ 
  PT & CES & Quality-adjusted & Without energy & kl & Reject CST & 1.017672 & 0.005739 & 1.000000 & 0.000000 & 0.000000 \\ 
  PT & CES & Quality-adjusted & With energy & kle & Reject CST & 1.027582 & 0.004508 & 0.902835 & 0.000000 & 0.097165 \\ 
  PT & CES & Quality-adjusted & With energy & lek & Reject CST & 1.016454 & 0.005790 & 1.000000 & 0.000000 & 0.000000 \\ 
  PT & CES & Quality-adjusted & With energy & ekl & Reject CST & 1.017327 & 0.005789 & 1.000000 & 0.000000 & 0.000000 \\ 
  UK & exp &  & Without energy &  & Reject CST &  & 0.023565 & 0.000000 & 0.000000 & 0.000000 \\ 
  UK & CES & Unadjusted & Without energy & kl & Adhere to CST & 1.006734 & 0.020914 & 0.300000 & 0.700000 & 0.000000 \\ 
  UK & CES & Unadjusted & Without energy & kl & Reject CST & 0.977872 & 0.017904 & 0.436298 & 0.563702 & 0.000000 \\ 
  UK & CES & Unadjusted & With energy & kle & Reject CST & 0.989712 & 0.013857 & 0.445243 & 0.554757 & 0.000000 \\ 
  UK & CES & Unadjusted & With energy & lek & Reject CST & 0.982919 & 0.020230 & 0.570049 & 0.134387 & 0.295564 \\ 
  UK & CES & Unadjusted & With energy & ekl & Reject CST & 0.985088 & 0.022682 & 0.254298 & 0.738243 & 0.007460 \\ 
  UK & CES & Quality-adjusted & Without energy & kl & Adhere to CST & 1.008638 & 0.013592 & 0.300000 & 0.700000 & 0.000000 \\ 
  UK & CES & Quality-adjusted & Without energy & kl & Reject CST & 0.983725 & 0.001956 & 0.628728 & 0.371272 & 0.000000 \\ 
  UK & CES & Quality-adjusted & With energy & kle & Reject CST & 0.980315 & 0.007103 & 0.426684 & 0.421804 & 0.151512 \\ 
  UK & CES & Quality-adjusted & With energy & lek & Reject CST & 0.968799 & 0.007115 & 0.469167 & 0.144017 & 0.386817 \\ 
  UK & CES & Quality-adjusted & With energy & ekl & Reject CST & 0.981695 & 0.011338 & 0.305749 & 0.642022 & 0.052229 \\ 
   \hline
\end{tabular}
}
\end{table}

%
% latex table generated in R 3.2.0 by xtable 1.7-4 package
% Wed Jul  8 16:46:02 2015
\begin{table}[ht]
\centering
\caption{Model parameters for all CES models.} 
\label{tab:CES_coeffs_sigmas}
{\tiny
\begin{tabular}{llllllrrr}
  \hline
Country & model & flavor & energy & nest & cst & sigma\_1 & sigma & mse \\ 
  \hline
PT & exp &  & Without energy &  & Reject CST &  &  & 0.013359 \\ 
  PT & CES & Unadjusted & Without energy & kl & Adhere to CST & 0.665163 &  & 0.011450 \\ 
  PT & CES & Unadjusted & Without energy & kl & Reject CST & 0.173623 &  & 0.001113 \\ 
  PT & CES & Unadjusted & With energy & kle & Reject CST & 0.078512 & 1.747120 & 0.000746 \\ 
  PT & CES & Unadjusted & With energy & lek & Reject CST & 0.398887 & 0.013645 & 0.000588 \\ 
  PT & CES & Unadjusted & With energy & ekl & Reject CST & 0.005193 & 0.186281 & 0.000985 \\ 
  PT & CES & Quality-adjusted & Without energy & kl & Adhere to CST & 0.399944 &  & 0.009694 \\ 
  PT & CES & Quality-adjusted & Without energy & kl & Reject CST & 0.017511 &  & 0.000804 \\ 
  PT & CES & Quality-adjusted & With energy & kle & Reject CST & 0.017991 &     Inf & 0.000792 \\ 
  PT & CES & Quality-adjusted & With energy & lek & Reject CST & 0.017595 & 0.005358 & 0.000812 \\ 
  PT & CES & Quality-adjusted & With energy & ekl & Reject CST & 0.017013 &  & 0.000817 \\ 
  UK & exp &  & Without energy &  & Reject CST &  &  & 0.001212 \\ 
  UK & CES & Unadjusted & Without energy & kl & Adhere to CST & 0.509524 &  & 0.000491 \\ 
  UK & CES & Unadjusted & Without energy & kl & Reject CST & 0.500000 &  & 0.000326 \\ 
  UK & CES & Unadjusted & With energy & kle & Reject CST & 0.720815 & 0.009391 & 0.000223 \\ 
  UK & CES & Unadjusted & With energy & lek & Reject CST &     Inf & 0.465188 & 0.000289 \\ 
  UK & CES & Unadjusted & With energy & ekl & Reject CST & 0.103338 & 1.340508 & 0.000281 \\ 
  UK & CES & Quality-adjusted & Without energy & kl & Adhere to CST & 0.545219 &  & 0.001207 \\ 
  UK & CES & Quality-adjusted & Without energy & kl & Reject CST & 0.607601 &  & 0.000571 \\ 
  UK & CES & Quality-adjusted & With energy & kle & Reject CST & 0.611818 & 0.014357 & 0.000267 \\ 
  UK & CES & Quality-adjusted & With energy & lek & Reject CST &     Inf & 0.611994 & 0.000380 \\ 
  UK & CES & Quality-adjusted & With energy & ekl & Reject CST & 0.190138 & 1.247783 & 0.000301 \\ 
   \hline
\end{tabular}
}
\end{table}

%
Tables~\ref{tab:DSRmse_CESkle}--\ref{tab:DSRmse_CESekl} show $\Delta \lambda$ and $\Delta mse$ 
results for CES models with various nestings.
%
% latex table generated in R 3.2.0 by xtable 1.7-4 package
% Wed Jul  8 16:46:02 2015
\begin{table}[ht]
\centering
\caption{$\Delta \lambda$ and $\Delta mse$ for CES models with ($kl$)$e$ nesting.} 
\label{tab:DSRmse_CESkle}
{\tiny
\begin{tabular}{llllllrr}
  \hline
Country & model & flavor & energy & nest & cst & Dlambda & Dmse \\ 
  \hline
PT & exp &  & Without energy &  & Reject CST & 0.000000 & 0.000000 \\ 
  PT & CES & Unadjusted & Without energy & kl & Adhere to CST & $-$0.015683 & $-$0.001908 \\ 
  PT & CES & Unadjusted & Without energy & kl & Reject CST & $-$0.022103 & $-$0.012246 \\ 
  PT & CES & Unadjusted & With energy & kle & Reject CST & $-$0.024769 & $-$0.012613 \\ 
  PT & CES & Quality-adjusted & Without energy & kl & Adhere to CST & $-$0.025377 & $-$0.003665 \\ 
  PT & CES & Quality-adjusted & Without energy & kl & Reject CST & $-$0.028768 & $-$0.012555 \\ 
  PT & CES & Quality-adjusted & With energy & kle & Reject CST & $-$0.029999 & $-$0.012566 \\ 
  UK & exp &  & Without energy &  & Reject CST & 0.000000 & 0.000000 \\ 
  UK & CES & Unadjusted & Without energy & kl & Adhere to CST & $-$0.002651 & $-$0.000721 \\ 
  UK & CES & Unadjusted & Without energy & kl & Reject CST & $-$0.005661 & $-$0.000886 \\ 
  UK & CES & Unadjusted & With energy & kle & Reject CST & $-$0.009708 & $-$0.000989 \\ 
  UK & CES & Quality-adjusted & Without energy & kl & Adhere to CST & $-$0.009973 & $-$0.000004 \\ 
  UK & CES & Quality-adjusted & Without energy & kl & Reject CST & $-$0.021609 & $-$0.000641 \\ 
  UK & CES & Quality-adjusted & With energy & kle & Reject CST & $-$0.016463 & $-$0.000944 \\ 
   \hline
\end{tabular}
}
\end{table}

%
% latex table generated in R 3.2.0 by xtable 1.7-4 package
% Wed Jul  8 16:46:02 2015
\begin{table}[ht]
\centering
\caption{$\Delta \lambda$ and $\Delta mse$ for CES models with ($le$)$k$ nesting.} 
\label{tab:DSRmse_CESlek}
{\tiny
\begin{tabular}{llllllrr}
  \hline
Country & model & flavor & energy & nest & cst & Dlambda & Dmse \\ 
  \hline
PT & exp &  & Without energy &  & Reject CST & 0.000000 & 0.000000 \\ 
  PT & CES & Unadjusted & Without energy & kl & Adhere to CST & $-$0.015683 & $-$0.001908 \\ 
  PT & CES & Unadjusted & Without energy & kl & Reject CST & $-$0.022103 & $-$0.012246 \\ 
  PT & CES & Unadjusted & With energy & lek & Reject CST & $-$0.026189 & $-$0.012771 \\ 
  PT & CES & Quality-adjusted & Without energy & kl & Adhere to CST & $-$0.025377 & $-$0.003665 \\ 
  PT & CES & Quality-adjusted & Without energy & kl & Reject CST & $-$0.028768 & $-$0.012555 \\ 
  PT & CES & Quality-adjusted & With energy & lek & Reject CST & $-$0.028717 & $-$0.012546 \\ 
  UK & exp &  & Without energy &  & Reject CST & 0.000000 & 0.000000 \\ 
  UK & CES & Unadjusted & Without energy & kl & Adhere to CST & $-$0.002651 & $-$0.000721 \\ 
  UK & CES & Unadjusted & Without energy & kl & Reject CST & $-$0.005661 & $-$0.000886 \\ 
  UK & CES & Unadjusted & With energy & lek & Reject CST & $-$0.003335 & $-$0.000923 \\ 
  UK & CES & Quality-adjusted & Without energy & kl & Adhere to CST & $-$0.009973 & $-$0.000004 \\ 
  UK & CES & Quality-adjusted & Without energy & kl & Reject CST & $-$0.021609 & $-$0.000641 \\ 
  UK & CES & Quality-adjusted & With energy & lek & Reject CST & $-$0.016450 & $-$0.000831 \\ 
   \hline
\end{tabular}
}
\end{table}

%
% latex table generated in R 3.2.0 by xtable 1.7-4 package
% Wed Jul  8 16:46:02 2015
\begin{table}[ht]
\centering
\caption{$\Delta \lambda$ and $\Delta mse$ for CES models with ($ek$)$l$ nesting.} 
\label{tab:DSRmse_CESekl}
{\tiny
\begin{tabular}{llllllrr}
  \hline
Country & model & flavor & energy & nest & cst & Dlambda & Dmse \\ 
  \hline
PT & exp &  & Without energy &  & Reject CST & 0.000000 & 0.000000 \\ 
  PT & CES & Unadjusted & Without energy & kl & Adhere to CST & $-$0.015683 & $-$0.001908 \\ 
  PT & CES & Unadjusted & Without energy & kl & Reject CST & $-$0.022103 & $-$0.012246 \\ 
  PT & CES & Unadjusted & With energy & ekl & Reject CST & $-$0.023766 & $-$0.012374 \\ 
  PT & CES & Quality-adjusted & Without energy & kl & Adhere to CST & $-$0.025377 & $-$0.003665 \\ 
  PT & CES & Quality-adjusted & Without energy & kl & Reject CST & $-$0.028768 & $-$0.012555 \\ 
  PT & CES & Quality-adjusted & With energy & ekl & Reject CST & $-$0.028718 & $-$0.012542 \\ 
  UK & exp &  & Without energy &  & Reject CST & 0.000000 & 0.000000 \\ 
  UK & CES & Unadjusted & Without energy & kl & Adhere to CST & $-$0.002651 & $-$0.000721 \\ 
  UK & CES & Unadjusted & Without energy & kl & Reject CST & $-$0.005661 & $-$0.000886 \\ 
  UK & CES & Unadjusted & With energy & ekl & Reject CST & $-$0.000883 & $-$0.000930 \\ 
  UK & CES & Quality-adjusted & Without energy & kl & Adhere to CST & $-$0.009973 & $-$0.000004 \\ 
  UK & CES & Quality-adjusted & Without energy & kl & Reject CST & $-$0.021609 & $-$0.000641 \\ 
  UK & CES & Quality-adjusted & With energy & ekl & Reject CST & $-$0.012227 & $-$0.000910 \\ 
   \hline
\end{tabular}
}
\end{table}

Figures~\ref{fig:DSRmse_CES_graph} and~\ref{fig:percDSRmse_CES_graph} summarize 
$\Delta \lambda$ and $\Delta mse$ 
results for CES models.
%
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}[H]
